Calculate cloud cover of scenes

### 2019-04-24 analysis/rmd/cloud-cover.Rmd
style

---
title: "Caclulcate cloud cover of scenes"
output: html_document
author: "Marc Becker"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = 'analysis/rmd/')
knitr::opts_chunk$set(fig.retina=3, fig.align = 'center', fig.width = 6.93, fig.height = 6.13,
                      out.width = "100%")

>>>>

---
title: "Calculate cloud cover of scenes"
output: html_document
author: "Marc Becker"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = 'analysis/rmd/')
knitr::opts_chunk$set(fig.retina = 3, fig.align = 'center', fig.width = 6.93, 
                      fig.height = 6.13, out.width = "100%")
